---
title: "FlightsOverYear_Yankee"
author: "Tyler Yankee"
date: "9/27/2022"
output: html_document
---

## Load data and relevant packages
```{r}
library(tidyverse)
library(here)
library(janitor)

df2017 = read_csv(here("data_raw", "airline_data_2017.zip")) %>% clean_names()
df2018 = read_csv(here("data_raw", "airline_data_2018.zip")) %>% clean_names()
df2019 = read_csv(here("data_raw", "airline_data_2019.zip")) %>% clean_names()
df2020 = read_csv(here("data_raw", "airline_data_2020.zip")) %>% clean_names()
df2021 = read_csv(here("data_raw", "airline_data_2021.zip")) %>% clean_names()
df2022 = read_csv(here("data_raw", "airline_data_2022.zip")) %>% clean_names()

# Make a list of these dataframes so that we can iterate through them later
# Indexing - 1=2017, 2=2018, 3=2019, 4=2020, 5=2021, 6=2022
years_list = list(df2017, df2018, df2019, df2020, df2021, df2022)

```

## Break down each year by month and look at flights for Southwest Airlines.
This could definitely be done better - I just don't have the most time right now.
Some ideas...

* Use select and join to get one data frame with all the years together (year is already a column) and only relevant info for each year (so departures_performed, month, maybe others?)
* Graph this dataframe, facet_wrap on year, and potentially color if that's not a clear enough split, so that it's all on one visualization and labeled rather than what is below.
```{r}
years_list = lapply(years_list, filter, carrier_name == "Southwest Airlines Co.", passengers > 0)

for(df in years_list)
{
  print(ggplot(df, aes(x = month)) + geom_bar(aes(weight = departures_performed)))
}

```


## Discussion of possibilities for visualizations

Assume to and from LGA.

* passengers over time for the total 6 years - get a time column, month * (year - 2017)
* could break this up by flight, by destination, etc.
* choose other airports and see if pattern is the same for your given airport - facet?
* Is your airline like the other airlines?

## New visualization
The new complete dataframe combines each year of data; filters to LaGuardia, Southwest Airlines, and flights with passengers; and adds a new column representing the total month since 2017.
```{r}
df_complete = rbind(df2017,df2018,df2019,df2020,df2021,df2022) %>%
  filter(origin == "LGA" | dest == "LGA", carrier_name == "Southwest Airlines Co.", passengers > 0) %>%
  select(departures_performed, passengers, carrier_name, origin, dest, year, month) %>%
  mutate(total_month = month + 12*(year - 2017))
df_complete %>% ggplot(aes(x = total_month)) + 
  geom_bar(aes(weight = passengers)) + 
  ggtitle("Passengers on Southwest Airline Flights from LaGuardia, 2017-2022") +
  xlab("Month (since 2017)") + ylab("Passengers")
```